Homicide Increases in the COVID-19 Era

### 2025-02-27 Draft1.qmd
added interpretation

## Histogram
```{r}
# fix mistake
evictions_la$Date.Received <- gsub("2205", "2025", evictions_la$Date.Received)

@@

ggplot(data = evictions_la_indexed_crimes, aes(x = index)) + 
  geom_histogram(aes(fill = high_low_crime), bins = nrow(unique_months)) +
  scale_x_continuous(breaks=unique_months$index,
        labels=unique_months$month_year) + 
  labs(x = "Month and Year of Eviction Notice Receipt", y = "Number of Evictions", title = "Monthly Frequency of Evictions and Crimes in the City of Los Angeles \nFebruary 2023 to February 2025", fill = "Crime Level") +
  ggthemes::scale_fill_fivethirtyeight() + 
  ggthemes::theme_stata(scheme = "s1mono") +
  theme(axis.text.x = element_text(angle = 300, vjust = 0.5, hjust = -.1),
        axis.title.x = element_text(vjust = -.75),
        plot.title = element_text(size=12))
```
### Interpretation

>>>>

## Number of Evictions and Crime Levels Per Month
```{r}
# fix mistake
evictions_la$Date.Received <- gsub("2205", "2025", evictions_la$Date.Received)

@@

evictions_la_indexed_crimes$high_low_crime <- as.factor(ifelse(evictions_la_indexed_crimes$num_crimes > avg_crimes, "Above Average", "Below Average"))

ggplot(data = evictions_la_indexed_crimes, aes(x = index)) + 
  geom_histogram(aes(fill = high_low_crime), bins = nrow(unique_months)) +
  scale_x_continuous(breaks=unique_months$index,
        labels=unique_months$month_year) + 
  labs(x = "Month and Year of Eviction Notice Receipt", y = "Number of Evictions", title = "Monthly Frequency of Evictions and Crimes in the City of Los Angeles \nFebruary 2023 to February 2025", fill = "Crime Level") +
  ggthemes::scale_fill_fivethirtyeight() + 
  ggthemes::theme_stata(scheme = "s1mono") +
  theme(axis.text.x = element_text(angle = 300, vjust = 0.5, hjust = -.1),
        axis.title.x = element_text(vjust = -.75),
        plot.title = element_text(size=12))
```
### Interpretation
This histogram plots the frequency of evictions in Los Angeles from February 2023 to February 2025, where the City of Los Angeles Housing Department has published case data. By summarizing both the crime and the evictions datasets by month, we see that the number of evictions was highest in early-mid 2023, and since, there have typically been slightly lower frequencies of evictions. Additionally, we split the number of crimes per month based on the average number of crimes of 14,439 to denote above and below average number of crimes per month. There is a clear split between March and April of 2024, as all months before that had above average crime, and all after had below average. Interestingly, the months where there is below average crime, seem to be the ones with slightly lower numbers of evictions.
